Analysis paper

### 2021-04-08 analysis/analysis.Rmd
add ridge plot for relative skill

@@

**To do**
- [] make a final decision (and document it somewhere) about how we want to exclude the Christmas period. Right now we are excluding forecast dates, but do not restrict target end dates in any way.

@@

>>>>

## Visualisation of data

truth <- dcast(df, ... ~ quantile, value.var = "prediction")[
  , .(location_name, target_end_date, target_type, true_value)] %>%
  unique()

truth <- truth[order(location_name, target_type, target_end_date)]

epi_classification <- function(actual_value, first_diff, threshold = 0.05) {
  out <- ifelse(first_diff > 0, "rising", "falling")
  out[abs(first_diff) < 0.05 * actual_value] <- "stable"
  return(out)
}

truth[, first_diff := c(NA, diff(true_value)), 
      by = c("location_name", "target_type")]
truth[, epi_class := epi_classification(true_value, shift(first_diff, -1)), 
      by = c("location_name", "target_type")]
truth[, shift_date := shift(target_end_date, -1), 
      by = c("location_name", "target_type")]
# truth[, second_diff := c(NA, diff(first_diff)), 
#       by = c("location_name", "target_type")]

ggplot(truth, aes(x = target_end_date)) + 
  geom_rect(aes(xmin = target_end_date, xmax = shift_date, ymin = -Inf, ymax = Inf, fill = epi_class), alpha = 0.2) +
  geom_line(aes(y = true_value, color = "truth")) + 
  geom_line(aes(y = first_diff, color = "first diff")) +
  labs(y = "value", x = "date") + 
  theme_light() + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  theme(legend.position = "bottom")

@@

- [] make a final decision (and document it somewhere) about how we want to exclude the Christmas period. Right now we are excluding forecast dates, but do not restrict target end dates in any way.

@@

### Model rankings in terms of scaled relative skill

```{r }
# scores by target type for 4 week ahead forecasts
scores <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "location_name", "forecast_date"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[model != "Baseline"]

ggplot(scores, aes(y = model, x = (scaled_rel_skill), 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  facet_wrap(location_name ~ target_type, scales = "free_x")
